---
title: "reading_data_from_the_web"
author: "Jingyi Yao"
date: "`r Sys.Date()`"
output: github_document
---

```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(rvest)
library(httr)
```

## Extracting tables

### 1. `read_html(url)` to read the webpage as an html file
```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

drug_use_html = read_html(url) # function in the rvest pacakge

drug_use_html

```

### 2. `html_table()` : pulls out all the tables in the html
```{r}
drug_use_html %>%
  html_table()

```

### 3. `first()`: pull out the first table
```{r}
table_marj = 
  drug_use_html %>% 
  html_table() %>% 
  first() 

table_marj

```

### 4. `slice(-1)` : get rid of the last row
```{r}
table_marj = 
  drug_use_html %>% 
  html_table() %>% 
  first() %>%
  slice(-1) 

table_marj

```



## CSS Selectors

```{r}
swm_html = 
  read_html("https://www.imdb.com/list/ls070150896/")

```

### 1. use the **selector gadget** to select the content we want

### 2. `html_elements(information generated by the gadget)` to read the same kind of data from html
```{r}
title_vec =   # get the titles
  swm_html %>%
  html_elements(".lister-item-header a") %>%
  html_text()

title_vec
```


```{r}
gross_rev_vec =   # gross revenue
  swm_html %>%
  html_elements(".ghost~ .text-muted+ span") %>%
  html_text()

gross_rev_vec
```


```{r}
runtime_vec =     # runtime
  swm_html %>%
  html_elements(".runtime") %>%
  html_text()

runtime_vec
```



## Using an API

### 1. `GET()` function used to read the **CSV** file
### 2. `content("parsed")` to clean the data (removing the front things)
```{r}
nyc_water_df= 
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.csv") %>% 
  content("parsed")   

nyc_water_df
```

### 3. `GET()` function used to read the **JSON** file
```{r}
nyc_water = 
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.json") %>% 
  content("text") %>%
  jsonlite::fromJSON() %>%
  as_tibble()

nyc_water

```


```{r}
brfss_smart2010 = 
  GET("https://chronicdata.cdc.gov/resource/acme-vg9e.csv",
      query = list("$limit" = 5000)) %>%   # limit the number of rows you get at a time
  content("parsed")

brfss_smart2010
```


```{r}
poke = 
  GET("http://pokeapi.co/api/v2/pokemon/1") %>%
  content()

poke$name
```


```{r}
poke$height
```

```{r}
poke$abilities
```


```{r}
poke [["stats"]]
```


```{r}
poke [["species"]]
```


```{r}
names(poke)
```



